---
title: "Perform and display clustering for computed tomography MLD profiles"
output: html_notebook
---



#Load up packages.
```{r}
pacman::p_load(Hmisc, coin, ggdendro, ggplot2)
```

#Get the data.
```{r}
raw_data <- read.csv2("C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/FD_data/Expi.csv")
raw_data2 <- read.csv("C:/Users/csuehs/Dropbox/SCANN'AIR_princeps/data-verification/Data_scannair_NA_corrections_isaetcarey_20170427.csv")
```


#Extract the appropriate variables. We are interested in raw FD values for attentuation at -850HU and according to two factors: 

* inspiratory versus expiratory measures;
* upper versus lower lung.
      ---slice 1
      ---slice 10
```{r}

df_fd <- data.frame(raw_data$numpat,
                  raw_data$I.850.H1,
                  raw_data$I.850.H10,
                  raw_data$I.850.L1,
                  raw_data$I.850.L10,
                  raw_data$E.850.H1,
                  raw_data$E.850.H10,
                  raw_data$E.850.L1,
                  raw_data$E.850.L10)

colnames(df_fd) <- c("patient",
                   "fd_i_up_1", 
                    "fd_i_up_10", 
                    "fd_i_lo_1", 
                    "fd_i_lo_10", 
                    "fd_e_up_1", 
                    "fd_e_up_10", 
                    "fd_e_lo_1", 
                    "fd_e_lo_10")



df_fd$fd_ei_up_1 <- df_fd$fd_e_up_1 / df_fd$fd_i_up_1
df_fd$fd_ei_up_10 <- df_fd$fd_e_up_10 / df_fd$fd_i_up_10

df_fd$fd_ei_lo_1 <- df_fd$fd_e_lo_1 / df_fd$fd_i_lo_1
df_fd$fd_ei_lo_10 <- df_fd$fd_e_lo_10 / df_fd$fd_i_lo_10


df_fd$fd_i_up <- (df_fd$fd_i_up_1 + df_fd$fd_i_up_10)/2
df_fd$fd_i_lo <- (df_fd$fd_i_lo_1 + df_fd$fd_i_lo_10)/2

df_fd$fd_e_up <- (df_fd$fd_e_up_1 + df_fd$fd_e_up_10)/2
df_fd$fd_e_lo <- (df_fd$fd_e_lo_1 + df_fd$fd_e_lo_10)/2

df_fd$fd_ei_up <- (df_fd$fd_ei_up_1 + df_fd$fd_ei_up_10)/2
df_fd$fd_ei_lo <- (df_fd$fd_ei_lo_1 + df_fd$fd_ei_lo_10)/2

df_fd$fd_i_bias <- (df_fd$fd_i_up - df_fd$fd_i_lo) / (df_fd$fd_i_up + df_fd$fd_i_lo) *200
df_fd$fd_e_bias <- (df_fd$fd_e_up - df_fd$fd_e_lo) / (df_fd$fd_e_up + df_fd$fd_e_lo) *200
df_fd$fd_ei_bias <- (df_fd$fd_ei_up - df_fd$fd_ei_lo) / (df_fd$fd_ei_up + df_fd$fd_ei_lo) *200

df_fd$fd_e_bias[is.nan(df_fd$fd_e_bias)] <- 0
df_fd$fd_ei_bias[is.nan(df_fd$fd_ei_bias)] <- 0



head(df_fd)

```

#Extract the appropriate MLD variables.
```{r}
df_mld <- data.frame(raw_data2$numpat,
                     raw_data2$I_MLD_H_1,
                     raw_data2$I_MLD_B_1,
                     raw_data2$E_MLD_H_1,
                     raw_data2$E_MLD_B_1)
    

colnames(df_mld) <- c("patient",
                      "mld_i_up",
                      "mld_i_lo",
                      "mld_e_up",
                      "mld_e_lo")

df_mld$mld_ei_up <- df_mld$mld_e_up/df_mld$mld_i_up
df_mld$mld_ei_lo <- df_mld$mld_e_lo/df_mld$mld_i_lo

df_mld$mld_i_bias <- (df_mld$mld_i_up - df_mld$mld_i_lo) / (df_mld$mld_i_up + df_mld$mld_i_lo) *200
df_mld$mld_e_bias <- (df_mld$mld_e_up - df_mld$mld_e_lo) / (df_mld$mld_e_up + df_mld$mld_e_lo) *200
df_mld$mld_ei_bias <- (df_mld$mld_ei_up - df_mld$mld_ei_lo) / (df_mld$mld_ei_up + df_mld$mld_ei_lo) *200


head(df_mld)

```


#Create a data frame for clustering.
```{r}
df <- merge(df_mld, df_fd, by = "patient", all.x = TRUE)


df[,grep("_1", names(df))] <- NULL

#remove missing data cases

df <- df[complete.cases(df),]

head(df)
```


#Figure out the best number of clusters by examining drops in inertia.
```{r}
clust_me <- df
row.names(clust_me) <- df$patient
clust_me$patient <- NULL
clust_me[,grep("fd", names(clust_me))] <- NULL
clust_me <- scale(clust_me)
dist.res <- dist(clust_me, method = "euclidean")

#_________________________________________________________________________________create first dendrogram: ascending algorithm


#helpful website: http://www.sthda.com/english/wiki/determining-the-optimal-number-of-clusters-3-must-known-methods-unsupervised-machine-learning
#helpful website: http://larmarange.github.io/analyse-R/classification-ascendante-hierarchique.html        
#La fonction de base pour le calcul d'un dendrogramme est hclust en précisant le 
#critère d'aggrégation avec method. Dans notre cas, nous allons opter pour la 
#méthode de Ward appliquée au carré des distances (ce qu'on indique avec method 
#= "ward.D2"4, l'option method = "ward.D" correspondant à la version 
#« classique ») :


arbre <- hclust(dist.res, method = "ward.D2")
inertie <- sort(arbre$height, decreasing = TRUE)

pdf(file = "optimal_cluster_fd_number.pdf",
    width = 10,
    height = 5)

layout(matrix(c(1,2,2), nrow = 1, ncol = 3))

plot(inertie[1:10], type = "s", xlab = "Number of clusters", 
     ylab = "Inertia", lwd = 2)
abline(v = 2, lty=5, col = "red")
minor.tick(nx=2, tick.ratio=1)

plot(arbre,
     xlab = "Patients",
     ylab = "Height (dissimilarity)",
     sub = "",
     main = "",
     cex = 0.7, 
     labels = )
rect.hclust(arbre, k = 2)

dev.off()
```
#Now create rawdata subsets corresponding to each cluster. 
```{r}
#________________________________________________________________________________create a rawdata subsets for clusters


typo2 <- data.frame(cutree(arbre, 2))
colnames(typo2) <- "c2"
typo2$patient <- rownames(typo2)

df <- merge(df, typo2, by = "patient")


temp <- data.frame(raw_data2$numpat,
                   raw_data2$age,
                   raw_data2$BMI,
                   raw_data2$valeur_no_ex,
                   raw_data2$valeur_no_alveo,
                   raw_data2$VEMSp_1,
                   raw_data2$CVFp_1,
                   raw_data2$VEMS.CVF_1,
                   raw_data2$ACQ6)

colnames(temp) <- c("patient",
                    "age",
                    "bmi",
                    "feno",
                    "fano",
                    "fev1",
                    "fvc",
                    "f.f",
                    "acq")

temp$acq <- as.numeric(as.character(temp$acq))

df <- merge(df, temp, by = "patient")

c1 <- subset(df, c2 == 1)
c2 <- subset(df, c2 == 2)

css1 <- c1
css2 <- c2

css1$patient <- NULL
css2$patient <- NULL

css1$c2 <- NULL
css2$c2 <- NULL

css1$c3 <- NULL
css2$c3 <- NULL


```





#Get descriptive data for each cluster.
```{r}
eff <- function(x) {length(which(!is.na(x)))}
per_func <- function(x) {mean(x, na.rm = TRUE)*100}
quartile_1 <- function(x) {quantile(x, probs = seq(0,1,0.25), na.rm = TRUE)[2]}
quartile_3 <- function(x) {quantile(x, probs = seq(0,1,0.25), na.rm = TRUE)[4]}
shap <- function(x) {as.numeric(shapiro.test(x)[2])}

count<- sapply(css1, eff)
minimum <- sapply(css1, min, na.rm = TRUE)
maximum <- sapply(css1, max, na.rm = TRUE)
mean <- sapply(css1, mean, na.rm = TRUE)
st_d <- sapply(css1, sd, na.rm = TRUE)
median <- sapply(css1, median, na.rm = TRUE)
quartile_25p <- sapply(css1, quartile_1)
quartile_75p <- sapply(css1, quartile_3)
shapiro_p <- sapply(css1, shap)

options(scipen = 999)
c1_descriptives <- data.frame(count, minimum, maximum, mean, 
                                st_d, median, quartile_25p, quartile_75p, shapiro_p)

write.csv(c1_descriptives, file = "C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/Submission2_Investigative_Radiology/stats-tables/mldcluster_c1_descriptives.csv")
write.csv2(c1_descriptives, file = "C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/Submission2_Investigative_Radiology/stats-tables/mldcluster_c1_descriptives_csv2.csv")


count<- sapply(css2, eff)
minimum <- sapply(css2, min, na.rm = TRUE)
maximum <- sapply(css2, max, na.rm = TRUE)
mean <- sapply(css2, mean, na.rm = TRUE)
st_d <- sapply(css2, sd, na.rm = TRUE)
median <- sapply(css2, median, na.rm = TRUE)
quartile_25p <- sapply(css2, quartile_1)
quartile_75p <- sapply(css2, quartile_3)
shapiro_p <- sapply(css2, shap)

options(scipen = 999)
c2_descriptives <- data.frame(count, minimum, maximum, mean, 
                                st_d, median, quartile_25p, quartile_75p, shapiro_p)

write.csv(c2_descriptives, file = "C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/Submission2_Investigative_Radiology/stats-tables/mldcluster_c2_descriptives.csv")
write.csv2(c2_descriptives, file = "C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/Submission2_Investigative_Radiology/stats-tables/mldcluster_c2_descriptives_csv2.csv")


```

#Compare clusters 1 & 2.
```{r}
#________________________________________________________________________________compare clusters (quantitative)


ttest_pvalue <- function(x,y) {
    k <- t.test(x,y)
    as.numeric(k[3])}

wilcox_pvalue <- function(x,y) {
    k <- wilcox.test(x,y)
    as.numeric(k[3])}

permute_pvalue <- function(x,y) {
    grp_1 <- rep(1, length(x))
    grp_2 <- rep(2, length(y))
    val_1 <- data.frame(x, grp_1)
    colnames(val_1) <- c("XXX", "group")
    val_2 <- data.frame(y, grp_2)
    colnames(val_2) <- c("XXX", "group")
    dataa <- rbind(val_1, val_2)
    k <- independence_test(formula = XXX~group, data = dataa)
    pvalue(k)}

tt <- c(); wcmw <- c(); perm <- c(); vn <- c()

temp1 <- css1
temp2 <- css2


for (j in 1:dim(temp1)[2]){
    tt[j] <- ttest_pvalue(temp1[,j], temp2[,j])
    wcmw[j] <- wilcox_pvalue(temp1[,j], temp2[,j])
    perm[j] <- permute_pvalue(temp1[,j], temp2[,j])
    vn[j] <- colnames(temp1)[j]
}

variable <- vn

options(scipen = 999)
two_group_comparisons_12 <- data.frame(variable, tt, wcmw, perm)
colnames(two_group_comparisons_12) <- c("variable", "t-test", "Mann Whitney-Wilcoxon", "permutation")

write.csv(two_group_comparisons_12, file = "C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/Submission2_Investigative_Radiology/stats-tables/cluster_comparisons_fd_12.csv")
write.csv2(two_group_comparisons_12, file = "C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/Submission2_Investigative_Radiology/stats-tables/cluster_comparisons_fd_12_csv2.csv")

```


#Redraw the hierarchical dendrogram using ggdendro.
```{r}
ggdendrogram(arbre) 
    
```

#Get the position of each patient on the dendrogram.
```{r}
dhc <- as.dendrogram(arbre, hang=0.1)
ddata <- dendro_data(dhc, type="rectangle")

tree_pos <- data.frame(ddata$labels)
colnames(tree_pos) <- c("x", "y", "patient")

tree_pos$y <- NULL

df <- merge(df, tree_pos, by = "patient")    

```

#Divide age, bmi, fev1, fvc, f.f, acq, feno and fano (and everything else) into quartiles for color coding.
```{r}



q_fd_e_up <- df$fd_e_up
q_fd_e_up[df$fd_e_up == 0] <- 1
q_fd_e_up[df$fd_e_up != 0] <- 1+ as.integer(cut(df$fd_e_up[df$fd_e_up != 0], quantile(df$fd_e_up[df$fd_e_up != 0], probs=0:3/3), include.lowest = TRUE))
q_fd_e_up



q_fd_ei_up <- df$fd_ei_up
q_fd_ei_up[df$fd_ei_up == 0] <- 1
q_fd_ei_up[df$fd_ei_up != 0] <- 1+ as.integer(cut(df$fd_ei_up[df$fd_ei_up != 0], quantile(df$fd_ei_up[df$fd_ei_up != 0], probs=0:3/3), include.lowest = TRUE))
q_fd_ei_up





q_fd_e_bias <- df$fd_e_bias
q_fd_e_bias[df$fd_e_bias == -200] <- 1
q_fd_e_bias[df$fd_e_bias != -200] <- 1+ as.integer(cut(df$fd_e_bias[df$fd_e_bias != -200], quantile(df$fd_e_bias[df$fd_e_bias != -200], probs=0:3/3), include.lowest = TRUE))
q_fd_e_bias



q_fd_ei_bias <- df$fd_ei_bias
q_fd_ei_bias[df$fd_ei_bias == -200] <- 1
q_fd_ei_bias[df$fd_ei_bias != -200] <- 1+ as.integer(cut(df$fd_ei_bias[df$fd_ei_bias != -200], quantile(df$fd_ei_bias[df$fd_ei_bias != -200], probs=0:3/3), include.lowest = TRUE))
q_fd_ei_bias







df <- within(df, q_age <- as.integer(cut(age, quantile(age, probs=0:4/4), include.lowest = TRUE)))
df <- within(df, q_bmi <- as.integer(cut(bmi, quantile(bmi, probs=0:4/4), include.lowest = TRUE)))
df <- within(df, q_acq <- as.integer(cut(acq, quantile(acq, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_fev1 <- as.integer(cut(fev1, quantile(fev1, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_fvc <- as.integer(cut(fvc, quantile(fvc, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_f.f <- as.integer(cut(f.f, quantile(f.f, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_feno <- as.integer(cut(feno, quantile(feno, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_fano <- as.integer(cut(fano, quantile(fano, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))

df <- within(df, q_fd_i_up <- as.integer(cut(fd_i_up, quantile(fd_i_up, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_fd_i_lo <- as.integer(cut(fd_i_lo, quantile(fd_i_lo, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_mld_i_up <- as.integer(cut(mld_i_up, quantile(mld_i_up, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_mld_i_lo <- as.integer(cut(mld_i_lo, quantile(mld_i_lo, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))

df$q_fd_e_up <- q_fd_e_up

df <- within(df, q_fd_e_lo <- as.integer(cut(fd_e_lo, quantile(fd_e_lo, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_mld_e_up <- as.integer(cut(mld_e_up, quantile(mld_e_up, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_mld_e_lo <- as.integer(cut(mld_e_lo, quantile(mld_e_lo, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))

df$q_fd_ei_up <- q_fd_ei_up
df <- within(df, q_fd_ei_lo <- as.integer(cut(fd_ei_lo, quantile(fd_ei_lo, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))

df <- within(df, q_mld_ei_up <- as.integer(cut(mld_ei_up, quantile(mld_ei_up, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_mld_ei_lo <- as.integer(cut(mld_ei_lo, quantile(mld_ei_lo, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))

df <- within(df, q_fd_i_bias <- as.integer(cut(fd_i_bias, quantile(fd_i_bias, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))


df$q_fd_e_bias <- q_fd_e_bias
df$q_fd_ei_bias <- q_fd_ei_bias


df <- within(df, q_mld_i_bias <- as.integer(cut(mld_i_bias, quantile(mld_i_bias, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_mld_e_bias <- as.integer(cut(mld_e_bias, quantile(mld_e_bias, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
df <- within(df, q_mld_ei_bias <- as.integer(cut(mld_ei_bias, quantile(mld_ei_bias, probs=0:4/4, na.rm = TRUE), include.lowest = TRUE)))
   
#dfpoints[,c(10:35)] <- as.character(dfpoints[,c(10:35)])
#str(dfpoints)

```


#Set up a variable with P values and colors.
```{r}
two_group_comparisons_12$et <- rep("P = ", length(two_group_comparisons_12$`Mann Whitney-Wilcoxon`))
two_group_comparisons_12$et[two_group_comparisons_12$`Mann Whitney-Wilcoxon` < 0.001] <- "P < "
two_group_comparisons_12$v <- round(two_group_comparisons_12$`Mann Whitney-Wilcoxon`, 3)
two_group_comparisons_12$v[two_group_comparisons_12$v == 0.000] <- 0.001
two_group_comparisons_12$eti <- paste(two_group_comparisons_12$et, sprintf("%.3f", two_group_comparisons_12$v))

two_group_comparisons_12$col <- rep("grey", length(two_group_comparisons_12$`Mann Whitney-Wilcoxon`))
two_group_comparisons_12$col[two_group_comparisons_12$`Mann Whitney-Wilcoxon` < 0.05] <- "black"



```



#Create variable line positions
```{r}



two_group_comparisons_12$rpos <- rep(0, length(two_group_comparisons_12$`Mann Whitney-Wilcoxon`))

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "age"] <- 1
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "bmi"] <- 2
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "acq"] <- 3

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fev1"] <- 5
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fvc"] <- 6
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "f.f"] <- 7

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "feno"] <- 9
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fano"] <- 10

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_i_up"] <- 12
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_i_lo"] <- 13

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_e_up"] <- 15
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_e_lo"] <- 16

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_ei_up"] <- 18
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_ei_lo"] <- 19

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_i_bias"] <- 21
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_e_bias"] <- 22
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "fd_ei_bias"] <- 23

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_i_up"] <- 26
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_i_lo"] <- 27

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_e_up"] <- 29
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_e_lo"] <- 30

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_ei_up"] <- 32
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_ei_lo"] <- 33

two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_i_bias"] <- 35
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_e_bias"] <- 36
two_group_comparisons_12$rpos[two_group_comparisons_12$variable == "mld_ei_bias"] <- 37

two_group_comparisons_12$rpos <- (two_group_comparisons_12$rpos + 1.5)*-1





```


#Create a dendrogram where the leaves are associated with variable quartiles.

```{r}
petitpois <- ggplot(segment(ddata)) +
    geom_segment(aes(x=-2, y=-10, xend=-2, yend=20), color="white")+
    geom_segment(aes(x=x, y=y, xend=xend, yend=yend))+
    geom_text(aes(x=x, y=-1, label=label, angle = 90, hjust=0), data=label(ddata))+
    geom_segment(aes(x=-1, y=1, xend=-1, yend=18), color = "grey", size=1, arrow = arrow())+
    annotate("text", x=-1.5, y=10, label = "Height (dissimilarity)", size = 8, color = "black", angle = 90)+
    
    theme(panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank())+
    
    
    geom_point(data = df, aes(x = x, y = -2.5, colour = q_age), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-2.5, label = "Age (years)", size=5, color="black")+

    geom_point(data = df, aes(x = x, y = -3.5, colour = q_bmi), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-3.5, label = "BMI (kg.m^-2)", size=5, color="black")+

    geom_point(data = df, aes(x = x, y = -4.5, colour = q_acq), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-4.5, label = "ACQ6 score", size=5, color="black")+
    
    
    
    
    geom_point(data = df, aes(x = x, y = -6.5, colour = q_fev1), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-6.5, label = "FEV1", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -7.5, colour = q_fvc), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-7.5, label = "FVC", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -8.5, colour = q_f.f), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-8.5, label = "FEV1/FVC", size=5, color="black")+
    
    
    
    geom_point(data = df, aes(x = x, y = -10.5, colour = q_feno), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-10.5, label = "FeNO", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -11.5, colour = q_fano), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-11.5, label = "CANO", size=5, color="black")+
    
    
    geom_point(data = df, aes(x = x, y = -13.5, colour = q_fd_i_up), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-13.5, label = "FD_I-850_up", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -14.5, colour = q_fd_i_lo), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-14.5, label = "FD_I-850_lo", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -16.5, colour = q_fd_e_up), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-16.5, label = "FD_E-850_up", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -17.5, colour = q_fd_e_lo), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-17.5, label = "FD_E-850_lo", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -19.5, colour = q_fd_ei_up), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-19.5, label = "FD_E/I-850_up", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -20.5, colour = q_fd_ei_lo), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-20.5, label = "FD_E/I-850_lo", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -22.5, colour = q_fd_i_bias), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-22.5, label = "FD_I_bias", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -23.5, colour = q_fd_e_bias), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-23.5, label = "FD_E_bias", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -24.5, colour = q_fd_ei_bias), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-24.5, label = "FD_E/I_bias", size=5, color="black")+
    
    
    
    geom_point(data = df, aes(x = x, y = -27.5, colour = q_mld_i_up), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-27.5, label = "MLD_I_up", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -28.5, colour = q_mld_i_lo), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-28.5, label = "MLD_I_lo", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -30.5, colour = q_mld_e_up), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-30.5, label = "MLD_E_up", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -31.5, colour = q_mld_e_lo), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-31.5, label = "MLD_E_lo", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -33.5, colour = q_mld_ei_up), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-33.5, label = "MLD_E/I_up", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -34.5, colour = q_mld_ei_lo), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-34.5, label = "MLD_E/I_lo", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -36.5, colour = q_mld_i_bias), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-36.5, label = "MLD_I_bias", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -37.5, colour = q_mld_e_bias), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-37.5, label = "MLD_E_bias", size=5, color="black")+
    
    geom_point(data = df, aes(x = x, y = -38.5, colour = q_mld_ei_bias), size = 7, shape = 19)+
    annotate("text", x=-2.8, y=-38.5, label = "MLD_E/I_bias", size=5, color="black")+
    
    
    
    
    
    geom_segment(aes(x=12.5, y=-39, xend=12.5, yend=0), color="blue")+
  
    scale_colour_gradient(low = "green", high = "hotpink", na.value = "white")+
    
    annotate("text", x=14.5, y=-26.2, label = "~underline('Clustering variables')", size=7, color="black", hjust=0.5, parse = TRUE)+
    
    annotate("text", x=32, y=two_group_comparisons_12$rpos, label = two_group_comparisons_12$eti, size=5, color=two_group_comparisons_12$col)+
   
    annotate("text", x=32, y=-0.2, label = "Cluster\n1 vs 2", size = 5, color="black")+
    
    annotate("text", x=4.6, y=12.6, label = "1", size = 10, color="darkgrey")+
    annotate("text", x=18.6, y=12.6, label = "2", size = 10, color="darkgrey")+
    
    
    theme(legend.position = "none")


petitpois
```


Save the graphic to appropriate files.
```{r}



     
pdf(file = "C:/Users/csuehs/Dropbox/SCANN'AIR_fractal_dimension/Submission2_Investigative_Radiology/figure_5/figure_5_drendrogram_dots_mld.pdf",
    height = 20, width = 15)

    petitpois
    
 
dev.off() 



```








